Research Review: \\The Extent of Adaptive Wild Introgression in Crops

### 2018-07-31 paper.tex
explained phasing
recency of introgressions

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and derivates of $d_{XY}$ including $G_{min}$ \citep{geneva2015} and $RND_{min}$ \citep{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants in a population and therefore lack power to detect very recent introgression, while the latter two overcome this limitation.
These statistics have been further developed by adding differentiation between both non-admixed ($A$) and admixed populations ($B$) and a source population ($C$) \citep{racimo2016}. 
For example, the $U_{A,B,C(w,x,y)}$ statistic summarizes the number of sites where an allele at frequency $y$ in the source population ($C$) has a frequency higher than $x$ in the admixed population ($B$) and lower than $w$ in the non-admixed population ($A$).
A similar statistic, $Q95_{A,B,C(w,y)}$, sets a hard cutoff at the $95^{th}$ percentile of allele frequency in the admixed population (B) \citep{racimo2016}.
Further modifications have allowed specification of more than one source population (see details in \citealt{racimo2016}).
Since differentiation-based methods can be calculated site-by-site, high-density, genome-wide data are not necessarily required.
However, accuracy of introgression estimates is improved with more comprehensive data.
Phased data are also not a prerequisite for differentiation-based methods.

@@

Phylogenetic relationships are applied to introgression detection using the ABBA-BABA statistic (also known as the D-statistic) and related metrics \citep{durand2011}.
These statistics make inferences regarding introgression based on genomic patterns of derived variants that are shared between populations or species.
While the D-statistic is best suited to detection of introgression at the genome level, elaborations of the D-statistic including $\hat{f_{d}}$ \citep{martin2015} and $D_{\textrm{FOIL}}$ tests \citep{pease2015} are capable of localizing introgression to specific chromosomal regions. 
The former is quite similar to the D-statistic but is based on allele frequencies, and the latter can identify donor and recipient lineages of introgression in a more complex, five-taxon phylogeny.
Like differentiation methods, phylogeny-based detection of introgression can be employed using low-density data.
However, because these methods require knowledge of whether an allele is ancestral or derived, data from a sufficiently diverged outgroup must be available.

>>>>

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and derivates of $d_{XY}$ including $G_{min}$ \citep{geneva2015} and $RND_{min}$ \citep{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants in a population and therefore lack power to detect very recent introgression, while the latter two overcome this limitation.
These statistics have been further developed by adding differentiation between both non-admixed ($A$) and admixed populations ($B$) and a source population ($C$) \citep{racimo2016}. 
For example, the $U_{A,B,C(w,x,y)}$ statistic summarizes the number of sites where an allele at frequency $y$ in the source population ($C$) has a frequency higher than $x$ in the admixed population ($B$) and lower than $w$ in the non-admixed population ($A$).
A similar statistic, $Q95_{A,B,C(w,y)}$, sets a hard cutoff at the $95^{th}$ percentile of allele frequency in the admixed population (B) \citep{racimo2016}.
Further modifications have allowed specification of more than one source population (see details in \citealt{racimo2016}).
Since differentiation-based methods can be calculated site-by-site, high-density, genome-wide data are not necessarily required.
However, accuracy of introgression estimates is improved with more comprehensive data.
Phased data (i.e., data aligned to maternal or paternal chromosomes) are also not a prerequisite for differentiation-based methods.

@@

Phylogenetic relationships are applied to introgression detection using the ABBA-BABA statistic (also known as the D-statistic) and related metrics \citep{durand2011}.
These statistics make inferences regarding introgression based on genomic patterns of derived variants that are shared between populations or species.
While the D-statistic is best suited to detection of introgression at the genome level, elaborations of the D-statistic including $\hat{f_{d}}$ \citep{martin2015} and $D_{\textrm{FOIL}}$ tests \citep{pease2015} are capable of localizing introgression to specific chromosomal regions.
The former is quite similar to the D-statistic but is based on allele frequencies, and the latter can identify donor and recipient lineages of introgression in a more complex, five-taxon phylogeny.
Like differentiation methods, phylogeny-based detection of introgression can be employed using low-density data.
However, because these methods require knowledge of whether an allele is ancestral or derived, data from a sufficiently diverged outgroup must be available.
%Using such methods as the D-statistic or HAPMIX to identify introgressant haplotypes and measure their length, for a given rate of linkage disequilibrium breakdown due to outcrossing frequency, one can estimate the recency of an introgression event.

The recency of an introgression event can be assessed by measuring patterns of linkage disequilibrium (LD) and identity by state (IBS) between the domesticated and wild populations.
Recent introgression will result in high LD \cite{chakraborty1988recombination} and genomic regions of high IBS \cite{gusev2011architecture}, both of which break down over time.
LD will break down faster in crops with high outcrossing frequencies due to greater recombination rates.
LD breakdown can be assessed with D-statistics or HAPMIX, and decrease in IBS can be assessed with with several tools, including the PLINK toolset \cite{purcell2007plink}.
Determining that a crop genome has low levels of LD or IBS with wild relatives can be cited as evidence that any introgressions are not recent (as in Poets et al. 2015 \cite{Poets2015).
